---
Reproducible Research: Peer Assessment 1
author: "FFouedjio"
date: "June, 2015"
---
###About
The github repo with RMarkdown source code: https://github.com/ffouedjio/RepData_PeerAssessment1

## Loading and preprocessing the data

```{r}
if(!file.exists("RepData_PeerAssessment1")){dir.create("RepData_PeerAssessment1")}
setwd("./RepData_PeerAssessment1/")
FileUrl<- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
download.file(FileUrl,destfile = "./activity.zip",method = "libcurl")
unzip("activity.zip")
data=read.csv("activity.csv",na.strings = "NA")
str(data)
data$date<-as.Date(data$date)
```


## What is mean total number of steps taken per day?

```{r} 
NumSteDay <- aggregate(steps ~ date, data, sum)
hist(NumSteDay$steps, main = "Daily Total Number of Steps", col="blue", xlab="Number of Steps")
Mean_NumSteDay<- mean(NumSteDay$steps)
Median_NumSteDay <- median(NumSteDay$steps)
```

The `mean` is `r Mean_NumSteDay` and the `median` is `r Median_NumSteDay`.

## What is the average daily activity pattern?


```{r}
MeaInvDay<-aggregate(steps ~ interval, data, mean)
plot(MeaInvDay$interval,MeaInvDay$steps,type="l",main="Average Number of steps per Interval",xlab="Interval", ylab="Number of Steps")
MaxInt <- MeaInvDay[which.max(MeaInvDay$steps),1]
```

The 5-minute interval, on average across all the days in the data set, containing the maximum number of steps is `r MaxInt`.

## Impute missing values. Compare imputed to non-imputed data.


```{r}
summary(data)
NumMisData <- sum(is.na(data$steps))
datan<-data    

for(i in 1:nrow(datan))
{
  Val=datan[i,"interval"]
  Num<-which(MeaInvDay[,"interval"]==Val)
  if(is.na(datan[i,"steps"])){datan[i,"steps"]<-MeaInvDay[Num,"steps"]}
}

NumSteDayn <- aggregate(steps ~ date, datan, sum)
hist(NumSteDayn$steps, main = "Daily Total Number of Steps (after Processing Misssing Values)", col="blue", xlab="Number of Steps")
Mean_NumSteDayn<- mean(NumSteDayn$steps)
Median_NumSteDayn <- median(NumSteDayn$steps)

hist(NumSteDay$steps, main = paste("Total Steps Each Day"), col="red", xlab="Number of Steps", add=T)
legend("topright", c("Imputed", "Non-imputed"), col=c("blue", "red"), lwd=10)

MeaDiff <- Mean_NumSteDayn - Mean_NumSteDay
MedDiff <- Median_NumSteDayn - Median_NumSteDay
TotDif <- sum(NumSteDayn$steps) - sum(NumSteDay$steps)
```

* The imputed data mean is `r Mean_NumSteDayn`
* The imputed data median is `r Median_NumSteDayn`
* The difference between the non-imputed mean and imputed mean is `r MeaDiff`
* The difference between the non-imputed mean and imputed mean is `r MedDiff`
* The difference between total number of steps between imputed and non-imputed data is `r TotDif`. 


## Are there differences in activity patterns between weekdays and weekends?
``` {r}
weekdays <- c("Monday", "Tuesday", "Wednesday", "Thursday", 
              "Friday")
datan$dow = as.factor(ifelse(is.element(weekdays(as.Date(datan$date)),weekdays), "Weekday", "Weekend"))
NumSteIntn <- aggregate(steps ~ interval + dow, datan, mean)

library(lattice)

xyplot(NumSteIntn$steps ~ NumSteIntn$interval|NumSteIntn$dow, main="Average Steps per Day by Interval",xlab="Interval", ylab="Steps",layout=c(1,2), type="l")

```
